### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	09:44:51	(Tue18.Mar)

Further details are provided in 2.}

@@

\ai{Thank you for pointing this out, we agree that this should be clarified. The array configuration produce the first grating lobes at $\theta = \text{arcsin}(\lambda M/D) = 23.5^\circ$, but this is not a problem since the element opening angle is $25^\circ$ ($\theta\in[12.5^\circ,12.5^\circ]$) at $f_c=100$\;kHz. In the paper we addition we perform sidescan imaging where only very narrow beams need to be beamformed. These details are now included in the paper.}

>>>>

Further details are provided in 2. A sentence elaborating on the element spacing has been added in section IV first paragraph; where the HISAS1030 is introduced.}

@@

\ai{Thank you for pointing this out, we agree that this should be clarified. The array configuration produce the first grating lobes at $\theta = \text{arcsin}(\lambda M/D) = 23.5^\circ$, but this is not a problem since the element opening angle is $25^\circ$ ($\theta\in[12.5^\circ,12.5^\circ]$) at $f_c=100$\;kHz. In the paper we addition we perform sidescan imaging where only very narrow beams need to be beamformed. These details are now included in the paper, some in the 5th paragraph of the introduction and some in the first paragraph of section IV.}
